%\documentclass[a4paper,12pt]{scrartcl}
\documentclass[Main]{subfiles}


\title{Pezzi temporanei e parti eliminate dalla tesi. }
\author{Toninus}
%\input{Preamble}
\begin{document}


%  Titolo
\maketitle
\begin{abstract}
	Sono un accumulatore.\\
	Tutti i mezzi testi, mezze intuizioni che non ho tradotto o a cui non ho trovato posto nella tesi le metto qui dentro.\\
	\vspace{2mm}
	La soluzione ideale sarebbe quella di creare un riquadro condizionale (tipo ifndef di c++) con una flag iniziale, osservazioni e mezze intuizioni potrebbero essere messe o nascoste in fase di compilazione.
	
\end{abstract}
%  Indice
\tableofcontents
%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
%/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/

%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
\chapter{Introduction}
%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
Devo fare un'introduzione soft, devo parafrasare i migliori.

\begin{Warning}
CD: Primer: \\

Quantum electrodynamics and the so-called standard model of particles have been experimentally verified to an outstanding degree of precision and allowed us to have an almost fully satisfactory and unified description of the electro-weak forces. 
It is striking that, to the inherent quantum nature of the description of elementary particles, it is opposed the structure of a classical theory, proper of general relativity. 
It is almost unanimously accepted that this quandary can be solved by developing a quantum version of Einstein’s theory, which is often dubbed as quantum gravity. Yet, despite countless efforts, a quantum theory of the gravitational interaction remains elusive at best.

Nonetheless, the quest to finding a quantum theory of gravity often lead the community to neglect the
existence of an intermediate regime which has acquired only recently a renewed relevance. As a matter fact,both quantum electrodynamics, the standard model of particles, as well as all the quantum theories thought in the standard undergraduate courses, are formulated under the assumption that the underlying background is Minkowski spacetime.

Yet, if we take into account the lesson of general relativity, Minkowski spacetime is a rather special case of a Lorentzian manifold, which solves Einstein’s equations only in absence of matter. At the same time, changing the structure of the background might look at first glance as an hazard. On the one hand, unless in very extreme conditions such as in a neighbourhood of a black hole, the gravitational effects are negligible and no direct evidence of the necessity to modify the spacetime metric has emerged in the experiments based at the high energy accelerators. On the other hand, the high degree of symmetry of the Minkowski metric, encoded in the Poincar´
e group, makes the formulation of any
quantum field theory technically much easier then the counterpart on an arbitrary Lorentzian background. Basic tools such as Fourier transform have no meaning nor counterpart as soon as we consider a manifold endowed with a non trivial metric.

For these reasons, the development of the so-called quantum field theory on curved backgrounds looked often more as a mere intellectual curiosity rather than a stringent necessity. This perception has drastically changed in the last twenty years or so, particularly thanks to the advances in our understanding of the Universe as we observe it. Cosmology has become one of the leading branches of theoretical physics, mostly because it offers the possibility to interface the models built so far with a plethora of experimental data. 
Since the formulation of theories like inflation, it has become increasingly clear not only that the matter description via quantum fields has to be taken into account, but also that, due to the large scales involved (both spatially and temporally), the presence of a non trivial background must be accounted for. Although gravity is still weak enough to justify a classical description of such force, the effects of a non Minkowskian metric on the quantum fields are no longer negligible.

At this stage, one should seek a formulation, based on suitable first principles, which can be applied to the largest possible class of backgrounds.  To this extent, in this thesis we will adopt the algebraic approach. 
Algebraic quantum field theory is proven to be the most promising way to reach a general and mathematical rigorous description of the foundations of quantum fields on a curved background.
Contemporary quantum field theory is mainly developed as quantization of classical fields and AQFT is not an exception.
In this case, the criteria to provide a proper quantization procedure are based on a set of axioms, first written down by Haag and Kastler for quantum theories on Minkowski spacetime and adapted to a curved background setting by Dimock.

These methods are known, respec- tively, as the covariant phase space formalism3–5 and the Peierls bracket. 


\end{Warning}



\begin{Warning}
Khavkine:\\

A classical field theory is essentially defined by a local variational principle for a given set of dynamical fields on a given spacetime manifold. 
The variational principle determines a set of partial differential equations (PDEs), the equations of motion, to be emposed on the dynamical fields. 
The equations of motion are typically hyperbolic (or can be made so with gauge fixing if gauge invariance is present).
What distinguishes variational PDEs among the more general class of hyperbolic PDEs is that their solution spaces can be naturally endowed with symplectic and hence Poisson structure, making it into a phase space. 
The algebra of smooth functions on the phase space with the corresponding Poisson bracket then constitutes the Poisson algebra of observables. The existence of this algebraic formulation is what allows for quantization. It is clear that the symplectic and Poisson structure on its phase space is a crucial ingredient in the description of a classical field theory. 
The most common way of building these structures is via the canonical formalism which requires an explicit choice of a time function, even when no one such choice is natural, and the application of a Legendre transform, which may be only ambiguously defined, for instance, in the presence of gauge invariance. 
However, it is also well known that both can be defined completely covariantly (that is, without choosing an ex- plicit time function or applying a Legendre transform) directly fromthe Lagrangian, without going through the canonical formalism. 
These methods are known, respec- tively, as the covariant phase space formalism3–5 and the Peierls bracket. 
They are clearly preferable when the canonical formalism explicitly breaks some of the natural symmetries of the theory (any relativistic theory is an example). 
The symplectic 2-form and the Poisson bivector constructed in this way are equivalent (they are mutual inverses). 
Despite the covariance of both constructions, until recently, their equivalence was only known via the intermediary of the non-covariant canonical formalism. 
That is, until Forger and Romero provided an elegant, completely covariant proof of the equivalence in the case of a scalar field.
In this review, we describe in depth the constructions of symplectic and Poisson structures of classical field theory, as well as their equivalence, all in a covariant way. 
A novel contribution of our exposition is an extension of the Forger-Romero argument to field theories where constraints and gauge invariance are present. 
Another is that we do not restrict ourselves to the class of wave-like equations defined on Lorentzian manifolds (though that will be the main source of our examples). 
We also pay special attention to several aspects that are often omitted or left implicit in the existing literature. 
Neither the covariant phase space nor the Peierls constructions are automatic. 
That is, besides a given Lagrangian density, several conditions must be fulfilled for the corresponding formulas to make sense.
We make these conditions explicit in both cases: existence of a Cauchy surface and spacelike compact support for solutions, in the construction of the symplectic structure, and existence of hyperbolic PDE system, with retarded and advanced Green functions, closely related to the equations of motions, in the construction of the Poisson structure. 
Furthermore, the statement of equivalence also requires a certain sufficient condition on the cohomological properties of the constraint and gauge generator differential operators. 
Note that we restrict our attention to the geometric and algebraic aspects of the constructions and systematically avoid analytical details.
In particular, the con- struction of the space of solutions of a PDE system on a spacetime of dimension greater than one (which corresponds to an ordinary mechanical system) requires a theory of infinite dimensional differential geometry. 
We treat the minimal amount of the needed infinite dimensional geometry in a formal way. 
On the other hand, an honest attempt to present the relevant functional analytical details can be found in Refs. 11–14. Our results could then form the core identities of a future investigation along similar lines that could extend them beyond the formal level.


Al che Khavkine procede con un'analisi storica molto dettagliata partendo dalle singole origini di ogni aspetto della teoria.
Non si tratta della modesta analisi delle fonti fatta da me che essenzialmente è partita da Peierls, passata per dewitt, e dopo si è focalizzata su scritti degli ultimi 20 anni, Marolf, Forger Romero ecc.

The canonical formalism in mechanics15–19 (what we would now call the construc- tion of the symplectic and Poisson structures on the phase space of a mechanical system) has a long history and is most closely associated with the names of Hamil- ton and Jacobi. Though, undoubtedly, its roots go back even to Lagrange. Its main features are (a) the identification of the phase space with the space of initial data and (b) the use of the Legendre transform to determine special coordinates on the phase space in which the symplectic form takes a certain canonical form (hence naming the formalism). Because of the relation of Poisson brackets to quantization, the problem of the quantization of fields in the early 20th century required the translation (see for instance Refs. 1,20) of the canonical formalism from mechanics to field theories (multiple independent variables instead of just one).

Souriau, despite lack ofmany explicit references to his work. Perhaps his importance is not surprising, since he was one of the people responsible for abstracting (in the 1960s) the modern notion of a symplectic manifold as the appropriate arena for mechanics.19 In particular, the name of Souriau is closely associated to identifying the classical phase space with the set of solutions of the equations of motion, rather

\end{Warning}

\begin{Warning}
Forger ROmero\\

One of the most annoying flaws of the usual canonical formalism in field theory is its lack of manifest covariance, that is, its lack of explicit Lorentz invariance (in the context of special relativity) and more generally its lack of explicit invariance under space-time coordinate transformations (in the context of general relativity). 
Of course, this defect is built into the theory from the very beginning, since the usual canonical formalism represents the dynamical variables of classical field theory by functions on some spacelike hypersurface (Cauchy data) and provides differential equations for their time evolution off this hypersurface: thus it presupposes a splitting of space-time into space and time, in the form of a foliation of space-time into Cauchy surfaces.
As a result, canonical quantization leads to models of quantum field theory whose covariance is far from obvious and in fact constitutes a formidable problem: as a well known example, we may quote the efforts necessary to check Lorentz invariance in (perturbative) quantum electrodynamics in the Coulomb gauge. 
These and similar observations have over many decades nourished attempts to develop a fully covariant formulation of the canonical formalism in classical field theory, which would hopefully serve as a starting point for alternative methods of quantization.
Among the many ideas that have been proposed in this direction, two have come to occupy a special role. One of these is the “covariant functional formalism”, based on the concept of “covariant phase space” which is defined as the (infinite-dimensional) space of solu- tions of the equations of motion. This approach was strongly advocated in the 1980’s by Crnkovi´
c,Witten and Zuckerman [1–3] (see also [4]) who showed how to construct a symplectic structure on the covariant phase space of many important models of field theory (including gauge theories and general relativity), but the idea as such has amuch longer history. The other has become known as the “multisymplectic formalism”, based on the concept of “multiphase space” which is a (finite-dimensional) space that can be
defined locally by associating to each coordinate qi not just one conjugate momentumpi but n conjugate momenta pµ
i (µ = 1,... ,n), where n is the dimension of the underly-
ing space-time manifold. In coordinate form, this construction goes back to the classical work of De Donder and Weyl in the 1930’s [5, 6], whereas a global formulation was initiated in the 1970’s by a group of mathematical physicists, mainly in Poland [7–9] but also elsewhere [10–12], and definitely established in the 1990’s [13, 14]; a detailed exposition, with lots of examples, can be found in the GIMmsy paper [15]. The two formalisms, although both fully covariant and directed towards the same ultimate goal, are of different nature; each of them has its own merits and drawbacks.




\end{Warning}







%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
\chapter{Prereq Mate}
%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/


	\begin{Warning}
	(Primer)\\
	This review is organized as follows: In Section 2 we discuss the key geometrical concepts which lie
at the heart of the construction of quantum field theory on curved backgrounds, particularly the notion of globally hyperbolic spacetimes. In Section 3, we focus instead on the classical description of linear free field theories, whose dynamics is ruled by hyperbolic partial differential equations on vector bundles. In particular we will be interested in those equations which admit advanced and retarded Green operators.
	\end{Warning}	
	\begin{Warning}
		Stile: Intro lapiadaria ai 3 argomenti ( bundle cinematica di campo, Glob iper stage per descrivere dinamica di tipo propagativo, Operatori tipo onda). Poi smitragliata di definizioni come faceva Penati.
	\end{Warning}	
	



	\section{Fiber Bundles}
	\begin{Warning}
	(Primer)\\
	As a starting point and for the sake of completeness, we recall the definitions of a vector bundle and of
its sections. The latter play a distinguished role since sections represent the natural mathematical object to associate to the physical idea of a classical field. For a detailed discussion of these topics we refer the reader
	\end{Warning}
	\begin{Warning}
	(Advances)
	As a starting point we introduce the building block of any classical and quantum field theory:
	\end{Warning}
	
	
	
		Cosa Serve Dire?
			\subsection{Formal Definition}
			Parto dalla definizione degli smooth.\\
			per la tesi interessano solo i lisci e i vettoriali.\\
			trivialization charts\\
			bundlemorphism\\
			\begin{Warning}
				Forse è necessario parlare del cartesian product. così posso parlare dei tensor bundle e quindi definire il prodotto scalare tra fibrati come una mappa sul primo tensor product?
				vedi def 9 di advances
				
			\end{Warning}			
			
			\subsection{Sections}
			Definizione\\
			
Formal definition ed esempi smooth e bundle (tutto ciò che 

			\subsection{Jet Bundles}
				\url{https://en.wikipedia.org/wiki/Jet_bundle}
				


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Globally Hyperbolic SpaceTime}
		\begin{Warning}
		(ADVANCEs)\\
		Goal of this section is to introduce all geometric concepts and tools which are necessary to discuss both the classical dynamics and the quantization of a free quantum field on a curved background. We assume that the reader is familiar with the basic notions of differential geometry and, to a minor extent, of general relativity.
		\end{Warning}
			
		ricordare di parlare di :
		\\ Sezioni con supporto time, past , future, space - compact (fare schemino come in advances)

			\begin{Warning}
				Mettere solo le definizioni che uso prese dagli articoli di review delle Fonti
			\end{Warning}	
			Appunti che mi ero preso scrivendo il secono capitolo:
					
			This condition is strictly connected to the dynamic behaviour of the system.
	
		Glon iperbolic determina la fogliazione dello spazio tempo per superfici di cauchy
		
		questo da la possibilità della buona posizione dei problemi di cauchy.. fisicamente è la condizione minima per definire i dati iniziali dell'evoluzione dinamica.
		definisco data...			
		
		\begin{Warning}
			Far notare che minkowski e tanti esempi importanti sono GH
		\end{Warning}
		
		\begin{observation}
		(che serve dopo) lo spazio $R$ è banalmente iperbolico in quanto tutti i punti posso essere visti come superfici di cauchy.
		\end{observation}
		
	\section{Green Hyperbolic Operators}
		\begin{Warning}
		Rapporto con la condizione sugli operatori...		
		
	No!		La definizione di green hyperbolicity non garantisce invece l'esistenza e unicità del problema di cauchy associata
		
		e non solo, anche l'esistenza degli operatori di green associati che sono ingrediente fondamentale della costruzione di peierls

		M è glob iper e P è green iper per tener conto del comporatamento propagativo
		definire sup cauchy
		definire s-t iperbolico (solo la caratterizzazione di ammetre una sup di cauchy)
		definire op green iperbolico su spazio tempo iperbolico (cioè ha delle green ope)
		Propr di buona definizione esistenza e unicita della soluzione
		
		Di particolare ricorrenza fisica sono gli operatori normally iperbolic
		espressione in coordinate
		esempio K-g!
		\end{Warning}		
			\begin{Warning}
				Mettere solo le definizioni che uso prese dagli articoli di review delle Fonti
		\end{Warning}	
					\begin{Warning}
				Pensavo di utilizzare la definizione di Green hyperbolic data da Bar che si avvale del concetto di formally dual (che non richiede la presenza del pairing) invece di quella usata in Advances AQFT che richiede solo che ammetta almeno un $G^\pm$  per poi dimostrare tramite teorema che se è anche autoaggiunto vale l'unicità. Si tratta solo di una piccola sfumatura.. Deve essere chiarito che in tutto ciò che faccio interessano che $$\forall P \, \exists1!G^\pm$$.
				Che poi questa condizione derivi da GH secondo bar o Gh secondo dap+selfadj è una di quelle questioni propriamente matematiche che poco interessa ai fisici della commissione.
			\end{Warning}			
			
			\begin{Warning}
			Devo richiedere che il green operator sia unico? sia negli schemi di quantizzazione che nella definizione di peierls faccio largo uso dell'unicità. 
			Per provare questa unicità si passa per la definizione di una forma bilineare che permette di parlare di aggiunto formale e quindi avvalersi del teorema.
			\end{Warning}
			
		    Green-hyperbolic operators are not necessarily hyperbolic in any PDE-sense and that they cannot be characterized in general by well-posedness of a Cauchy problem. \cite{Terlaky2010} \cite{Bar2010}
		




%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
\chapter{Lagrangian systems e Pierls}
	\section{Presentazione in Astratto}
		Quando parlo della cinematica mi piacerebbe dare indicazioni sulla struttura matematica dello spazio delle configurazioni cinematiche:
			\begin{enumerate}
				\item costituisce una frechet manifold ( gli unici risultati che ho trovato sono quelli di Palais di "non linear global analysis"
				\item le curve parametrizzate sono le variazioni
				\item classi di equivalenza definiscono delle variazioni infinitesime che costituiscono lo spazio tangente allo spazio delle configurazioni cinematiche
				\item questo spazio tangente è isomorfo allo spazio delle sezioni del pullback rispetto alla sezione $\phi\in C$ del verical bundle (vedere forger romero)
				\item il problema dell'atlante e della rappresentazione delle sezioni in carta locale ( da scegliere sia sul total space E che sul base space M)
			\end{enumerate}
		Dovrei fare riferimento al teorema di Ostrowsky per giustificare il fatto che consideriamo solo il primo ordine. le langrangiana con termini cinetici esotici sono instabili ( nel senzo che non ammetto come soluzioni sezioni globali ma solo locali ).
		
		Attenzione: come definisco l'equazione del moto se il fibrato di configurazione non è vettoriale? nel senso: non mi serve tanto la definizione di + e x ma quello che mi serve è l'esistenza di un unico elemento nullo. Se manca questo manca la possibilità di poter definire un'equazione.
		
		Attenzione2: il motion operator credo che debba essere un bundlemorfismo cioè deve essere fiber preserving su ogni fibra determina un endomorfismo. ??? non va bene ho detto che agisce sulle sezioni!

		\begin{notationfix}
		For a given dynamical operator:%Given an equations of motion operator (Correzione CD)
		\begin{displaymath}
			P: \Conf \rightarrow \Conf
		\end{displaymath}
		The space
		\begin{displaymath}
		\gls{Sol} \coloneqq \ker(P) \subset \Conf
		\end{displaymath}
		containing all the smooth solutions is called \emph{"Space of Dynamical Configurations"}.
	\end{notationfix}
	
	\begin{Warning}
		Punto Cruciale : Richiedere che il fibrato di configurazione sia necessariamente un fibrato vettoriale (pag.1, pag.3, pag.16)\\
	No, il mio obbiettivo è di essere sufficientemente generico in modo che anche il problema della geodetica possa essere infilato in questa categoria.
		\\
		 Mi rendo conto che i conti non tornano. La falla principale è a pag.3 dove parlo di Kernel, il che non ha alcun senso visto che non ho modo di definire una sezione "zero". \\
		 Altro aspetto da sottolineare è che sui fibrati non vettoriali i concetti come sovrapposizione, perturbazione ecc.. possono essere definiti al massimo localmente, mai globalmente.
		\\
		Propongo dunque di definire il "Motion operator" P in modo da cogliere le proprietà cruciali del problema della geodetica:
			\begin{itemize}
			  	\item per ogni sezione ho tante rappresentazione in carta locale corrispondenti a tutte le combinazioni di "patch" (ammesso che vi corrisponda anche una trivializzazione locale) che posso scegliere sulla varietà base e sulla varietà fibra. Per ognuna di queste scelte associo alla sezione una funzione liscia da $R^m$ a $R^q$.\\

				\item Dunque ognuna di queste coppie di carte implica anche una rappresentazione di P come operatore dallo spazio delle funzioni lisce da $R^m$ a $R^q$ in se stesso. Chiamiamola $R(P): C^\infty -> C^\infty$
				\item Ammesso che il range di queste rappresentazioni contenga sempre lo 0  è sempre ben definita una motion equation (esclusivamente locale).
				\begin{displaymath}
					 R(P) \phi = 0
				\end{displaymath}
				\item  Ipotesi cruciale è che per coppie di rappresentazioni locali in qualche modo overlapping le soluzioni coincidano ( a meno di un cambio di coordinate) in modo che posso definiri sezioni locali che risolvono l'equazione in modo indipendente dalla carta locale scelta.
			\end{itemize}
			In altre parole vorei generalizzare quello che accade con le geodetiche dove ho una rappresentazione in carta dell'equazione geodetica per ogni carta locale. Questa rappresentazione ammette una unica soluzione (locale).Per come è definita l'equazione della geodetica si ha che la sua soluzione è indipendente dalla carta scelta.

			\vspace{3mm}
			Risposta:\\
			Secondo me è molto meno "grave" di quello che stai pensando. 
			Il punto fondamentale è il seguente. Se il fibrato non è vettoriale, puoi definire un operatore differenziale che, in carta locale, è una combinazione lineare di derivate. 
			Ciò che perdi è la struttura lineare se lo spazio di target non è uno spazio/fibrato vettoriale. 
			Ad esempio ha senso domandarsi cosa vuol dire $P\varphi = 0$, però $\varphi$ non è un elemento del kernel, in quanto la somma di due soluzioni non è nemmeno ben definita. Allo stesso tempo P non puoi chiamarlo operatore lineare. In pratica devi stare attento solo a togliere ogni riferimento alle strutture lineari tipiche degli spazi vettoriali fintanto che non lavori con fibrati vettoriali.
	\end{Warning}

	\section{Concrete Realization}
		\subsection{Fields}
			The field systems are a subset of the lagrangian systems:
			\begin{definition}[Linear Fields on curved Background]
				It's a Lagragian system $(E,\Lagrangian)$ such that:
				\begin{itemize}
					\item the configuration bundle $E\xrightarrow{\pi} M$ is a \underline{vector bundle}.
					\item the base manifold $M$ is a \underline{Globally Hyperbolic Spacetime}.
					\item the Euler-Lagrange operator $P= Q_\Lagrangian$ is a \underline{Green Hyperbolic operator}.
					\item For each Cauchy surface $\Sigma \subset M$ can be defined a well-posed Cauchy problem for the motion equation of $P$.\footnote{Green-hyperbolic operators are not necessarily hyperbolic in any PDE-sense and that they cannot be characterized in general by well-posedness of a Cauchy problem. \cite{Terlaky2010} \cite{Bar2010}}
				\end{itemize}
			\end{definition}
		But the other three condition are worth a deeper insight:
		\begin{itemize}
			\item 	\textbf{Vector Bundle Condition}
			\item 	\textbf{Global hyperbolicity condition.}
			\item 	\textbf{Green-Hyperbolicity condition.}
			\item 	\textbf{Cauchy condition.}\\
					While the existence of a Cauchy surface allows to assign the data of initial value problems, the forth condition ensure the well -posedness of the problem for on every Cauchy surface $\Sigma$. I.e:
					\begin{equation}\label{CauchyProblem}
							\begin{cases} P u = 0 \\ u = u_0 \\ \nabla_{\vec{n}}u= u_1 \end{cases}
					\end{equation}
					admit a unique solution $u\in \Gamma(E)$ for all $(u_0, u_1) \in \Gamma (\Sigma )\times \Gamma (\Sigma )$.		
		\end{itemize}

		\begin{observation}
			\begin{center}
				\textbf{Visione Globale}
			\end{center}
			\begin{itemize}
			\item Secondo bar e ginoux per parlare di campo classico non serve specificare nient'altro...
				\begin{itemize}
					\item la condizione di $\exists  1!$ operatore di green di $P$  insieme a quella di Essere un sistema lagrangiano è un requisito minimo  per definire senza ambiguità le parentesi di peierls.
					\item La buona definizione delle parentesi di Peierls è requistio algebrico per portare avanti la quantizzazione algebrica standard (come fa Dappiaggi): \\
					la condizione di green-hyperbolicity ( che garantisce di $\exists 1!\; E^\mp$ ma non che  $\exists 1!$ soluzione del PC) corredata della scelta di un pairing permette di quantizzare secondo lo schema algebrico
					\item La condizione di well-posedness del problema di cauchy da la possibilità di quantizzare secondo lo schema dei dati iniziali
				\end{itemize}
				\item in tutti questi casi la candizione di Globally -hyperbolic per lo spazio tempo sottostante è necessaria
			\end{itemize}
		\end{observation}
		
		\begin{example}
			in adv AQFT ci sono 3 realizzazioni concrete. Klein-Gordon e Proca soddisfano tutte le condizioni precedenti. Anche Dirac ma non è normally Hyperbolic, solo green
		\end{example}

	\subsection{Sistemi a finiti gradi (meccanica geometrica ordinaria)}
		Paragrafo in cui faccio vedere come è possibile vedere un sistema lagrangiano ordinario con un sistema lagrangiano di tipo campo quindi come un sotto-sotto-caso del sistema lagrangiano astratto.

		  % il fibrato non è vettoriale
		  % le configurazioni sono curve
		  % 
		  	Every system with discrete degrees of freedom can be seen as a trivial field system.
			The correspondence is easily done:
			\begin{itemize}
				\item Configuration bundle of the system is the trivial $E= Q \times \Real$ with base manifold $M=\Real$.
				\item The kinematic configuration are $\Conf=C^\infty(\Real,Q)$ i.e.all the possible parametrized functions on $Q$.
				\item The Larangian density is obtained evaluating the ordinary Lagrangian on the lifted curve:
					\begin{equation}
						\Lagrangian  [\gamma] \coloneqq \big( L \circ	\gamma^\textrm{lift} \big) dt  = \Lagrangian(t,\gamma^i,\dot{\gamma}^i)
					\end{equation}
	\end{itemize}
	\begin{Warning}
		devo mettere le conclusione scritte sul primo quaderno insieme a quelle messe nel secondo e poi ripetute a seguito della costruzione di peierls e a quella di quantizzazione ( nei miei appunti io ho fatto ogni singolo passo in generale e poi realizzato per i sistemi campo-curve. Per la stesura finale ho deciso di unire tutto insieme in questo ultimo capitolo (senza ripetere ogni volta che il fibrato è triviale con fibra Q, la varietà base è banalmente globally iperbolic in quanto R. tutti i punti di R sono superfici di cauchy ecc ecc)
	\end{Warning}
	
	\section{Recap Geometric Mechanics}
		
	\begin{Warning}	
	 La visione precedente è molto generale ma ci sono alcune strutture classiche che voglio replicare sul campo come la forma simplettica, le osservabili e le parentesi di poisson.
	 Mi sembra più chiaro vederle dopo aver raccontato queste.
	 
	Quindi devo parlare un po' di meccanica geometrica, di
	\begin{itemize}
		\item Spazio delle Fasi
		\item tautological 1-form
		\item simplectic form
		\item canonical coordinate and darboux theorem
		\item observable as smooth scalar field on the phase space
		\item poisson structure
	\end{itemize}
	\end{Warning}
	
	Attenzione: per quello che mi serve di seguito non mi interessa il discorso della forma simplettica canonica. Quella è la specifica forma simplettica della MECCANICA CLASSICA.\\
	Mi serve solo dire cos'è lo spazio delle fasi e gli osservabili classici.\\
	Faccio accenno al fatto che lo spazio delle fasi classico è naturlmente simplettico.\\
	Definisco quindi l'espressione astratta del sistema hamiltoniano come coppia varietà simplettica + Hamiltoniana.\\
	Fare riferimento che i sistemi hamiltoniani classici posso essere visti come un sottoinsime di quelli lagrangiani (vedi FOMM legendre and hyperregular lagrangia.\\
	Ma, far notare come il processo di quantizzazione della MQO richieda di spostarsi in questo punto di vista più astratto in quanto si basa sulla prescrizione di una diversa espressione delle parentesi di poisson, - quella in grado di implementare le CCR.\\
	
		\begin{proposition}[Possion Structure]
	
		\begin{itemize}
			\item $\{\cdot, \cdot\} = - \{\cdot, \cdot\}$ \emph{Skew-Simmetric}.
			\item $\{\cdot,\{\cdot, \cdot\}\} + \{\cdot,\{\cdot, \cdot\}\} + \{\cdot,\{\cdot, \cdot\}\} = 0$ \emph{Jacobi}
			\item $\{\cdot,\{\cdot, \cdot\}\}= f \{\cdot,\{\cdot, \cdot\}\} + g \{\cdot,\{\cdot, \cdot\}\}$ \emph{Liebniz}
\end{itemize}			
	
	\end{proposition}	
	
	\subsection{Caso Lineare}
		Ricapitolando le novità essenziali che ci saranno utili riguardano il procedimento di quantizzazione sono le seguenti:
		\begin{itemize}
			\item la forma simplettica è definita direttamente sui punti dello spazio delle fasi
			\item la forma simplettica si riproduce sullo spazio degli osservabili lineari ed è compatibile con la poisson
			\item siccome i punti dello spazio delle fasi possono essere messi in corrispondenza biunivoca con le soluzioni (sono i Data) la forma simplettica si trasporta anche su SOL
		\end{itemize}
	
	\section{Peierls Algorithm}
		\begin{Warning}
			\textbf{Possibili migliorie:}
				\begin{itemize}
					\item Aggiungere altre chiacchiere e marketing riguardo le  PB, vedere nelle fonti cosa dicono i sapienti
					\end{itemize}
		\end{Warning}
			\begin{observation}[Peierls Bracket vs Poisson Bracket]
		\begin{Warning}
	Paraphrasing an observation made by Sharan\cite{Sharan2010}:
	
	
		
	While the Poisson bracket between two observables a and b is defined on the whole phase space and is not dependent on the existence of a Hamiltonian, the Peierls bracket refers to a specific trajectory determined by a governing Lagrangian. 
	
	\end{Warning}
	\end{observation}	
	
	\begin{Warning}
		io ho cercato di usare termini diversi come disturbance, perturbation oppure disturbed, perturbed
		ma dare piccole sfumature di differenza
		
		Per la tesi non va bene perchè non sono tutti termini standard! (consiglio di CD)
	\end{Warning}
	
	\subsection{Non Linear Extension}
		non mi è evidente se la rappresentazione in coordinate di un operatore agente sulle sezioni si realizza in modo ovvio, ma non vedo nemmeno ostruzioni! Di sicuro l'operazione è ben definita per gli L.P.D.O visto che la definizione prevede proprio che su ogni carta locale trivilizzante l'operatore sia lineare alle derivate parziali.
	
	\section{Correzioni del Capo}
	>   1) Teorema di Ostro...(non ho capito come si chiama!) per motivare il fatto che ci limitiamo a considerare densità lagrangiane sul primo Jet.

Si tratta di Ostrogradsky, un matematico ucraino ed il problema è noto come instabilità di Ostrogradsky. In realtà non esiste una referenza esplicita in teoria dei campi perché è un problema molto più generale di ODE/PDE. Per assurdo la dimostrazione (e le referenze) date su Wikipedia sono ottime:

	\url{https://en.wikipedia.org/wiki/Ostrogradsky_instability}

     2) posso dire che su qualsiasi fibrato liscio lo spazio delle sezioni liscie è una varietà di Frechet? Se non posso dirlo globalmente potrei ridurmi localmente alla rappresentazione della sezione in carta locale, hai una reference bella dove si prova che lo spazio delle funzioni lisce tra due aperti di $R^n$ è una varietà di frechet?

Dipende tutto dalla fibra tipica del fibrato. Se è un fibrato vettoriale di rango finito, allora sì. Una referenza? Prova il libro di Michor "Convinient calculus" (credo sia il titolo giusto, l'autore è sicuramente lui)

		---oppure... teniamo presente che qualunque sia il fibrato liscio... localmente E = Rq x Rm è banale! quindi le sezioni locali su un aperto sono isomorfe a Cinfty (U) che è frechet...
		secondo me bisogna giocare su questo, non sulla linearità. il problema geodetico non riuscirò mai a vederlo come lineare.. però localmente è dato da tanti operatore uno per ogni aperto dell'atlante della varietà riemmaniana... in questi aperti l'equazione gedoetica prende la forma nota e il PC locale ammette un unica soluzione!
		Poi qua entrerebbe il problema dell'estensione della geodetica (completezza geodetica vedere fomm, jost o abate, \href{http://tinyurl.com/pcxbcqr}{wiki, teorema di hopf-rinow}
		Attenzione: il problema geodetico lo posso definire per aperti... ma la particolarità dell'equazione geodetica è che è compatibile per carte overlapping!
		Se devo specificare la natura dell'operatore del moto generico su fibrato generico ho parecchio da imbarcare... Di sicuro non si passa per attribuire al fibrati di configurazione una sezione "nulla" perchè non ha senso: quale sarebbe la sezione nulla nel caso delle geodetiche? l'annullamento è sempre una questione di carta....

     3)Operatore di Eulero Lagrange è sempre Globalmente Iperbolico nel caso della dinamica di sistemi lagrangiani a gradi di Libertà finiti?

Assolutamente no! Esistono anche lagrangiane non quadratiche nelle velocità ... è proprio il senso del lavoro di Ostrogradsky, ossia ci sono lagrangiane con equazioni del moto altamente instabili.


%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
\chapter{Algebraic Quantization}
%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
\section{Intro}
	Contemporary quantum field theory is mainly developed as quantization of classical fields. Classical field theory thus is a necessary step towards quantum field theory.\danger (Cito testualmente Mangiarotti, shardanashivly)
	
The \emph{"Quantization process"} has to be considered as an algorithm , in the sense of self-containing succession of instructions, that has to be performed in order to establish a correspondence between a classical field theory and its quantum counterpart.\\
\danger (forse l'nlab esprime la cosa meglio di me \url{http://ncatlab.org/nlab/show/quantization}. Sono d'accordo con il loro approccio ma non voglio usare la loro formulazione perchè in fondo ci sono arrivato anche da solo :P)


\danger\footnote{Frase che non mi piace ma voglio far presente che le realizzazioni dello schema algebrico sono molteplici!}
As said previously, the realization of the Algebraic scheme are many: Fedosov's procedure, by Deformation, Peierls' procedure, by Initial Data etc .
In the next section we review the last two.

\section{Algebraic quantization}
\subsection{Quantization with Peierls}
\danger Questo schema a passi rende bene sul quaderno ma non su latex... riorganizzo tutto in modo che ogni passo venga organizzato in section subsection eccetera.

\danger Attenzione: nello schema nel quaderno, al passo sulla costruzione dello spazio degli osservabili, ho usato una notazione che utilizza il mapping F tra sezioni e funzionali!

	Briefly the procedure can be resumed in few steps:
 	\begin{enumerate}
   		\item Classical Step\\
   			Has to be stated the mathematical structure of the classical theory under examination.
   			\begin{enumerate}
   				\item Kinematics: is encoded in the configuration bundle of the theory.
   					\begin{enumerate}
   						\item Specify the base manifold $M$. \\Has to be a Globally-Hyperbolic Space-time.
   						\item\label{Step:AuxiliaryStructure} Specify the Fiber and the total Space $E$ auxiliary structure, e.g: spin-structure or trasformation laws under diffeomorphism on the base space.\\$E$ has to be at least a vector bundle.
   					\end{enumerate}
   			
   				\item\label{Step:ClassicalDynamicsConditions} Dinamics: has to be specified the local coordinate expression of the motion operator $P: \Gamma^\infty (E)= \Conf \rightarrow \Conf$.
   				   	\begin{enumerate}
   						\item Is $P$ Green-hyperbolic?
   						\item Is $P$ derived from a lagrangian: $P=Q_\Lagrangian$? 
   					\end{enumerate}
   			\end{enumerate}
   			
   		\item Pre-Quantum Step
   		   	\begin{enumerate}
   				\item Pairing: construct a basic bilinear form on the space of kinematic configurations.
   					\begin{enumerate}
   						\item Choose $<\cdot,\cdot>$ a inner product on the bundle $E$.\\ 
						This is a parameter to be guessed. Generally this object is suggested by the auxiliary structures defined on the configuration bundle [\ref{Step:AuxiliaryStructure}].
   						\item Construct the pairing between sections with compact support intersection:
   							\begin{displaymath}
   								(X,Y) = \int_M <X,Y>_x d\mu(x)
   							\end{displaymath}
   						\item is $P$ formally self-adjoint in respect to this pairing?
   					\end{enumerate}
   					
   				\item Classical Observables: construct a set $\Obs$ of suitable classical observables.
   				   	\begin{enumerate}
   						\item Asantz on the off-shell functionals.\\
   							We define a class of linear functional on $\Conf$:
   							\begin{displaymath}
   								\Obs_0 \coloneqq \big\{ F_f: \Conf \rightarrow \Real \:\vert
   								\: F_f(\phi)=\int_M ( f, \phi) d\mu \; , f \in \Gamma_0^\infty(E)	\big\}
   							\end{displaymath}
   							Satisfying the conditions of good definition:
   							\begin{itemize}
   								\item Faithfully representation of the vector space $\Gamma_0^\infty(E)$ (bijective map).
   								\item Separation of the configuration space $\Conf$.   								
   							\end{itemize}
   						\item Domain restriction of the functionals in $\Obs_0$ from $\Conf$ to $\Sol$:
   							\begin{displaymath}
   								\Obs_0\vert_\Sol \coloneqq \big\{F_f\vert_\Sol \big \vert F_f \in \Obs_0 \big\}
   							\end{displaymath}
   							Such that: 
   							\begin{itemize}
   								\item $\Obs_0\vert_\Sol$ met the separability condition.
   								\item The correspondence with  $\Gamma_0^\infty(E)$ is no more injective:
   									\begin{displaymath}
   										\ker \big( \Obs_0 \mapsto \Obs_0\vert_\Sol \big) \coloneqq N \equiv P \big( \Gamma_0^\infty (E) \big)
   									\end{displaymath}
   								\item Define the classical observables space as the quotient:
   									\begin{displaymath}
   										\Obs \coloneqq \frac{\Obs_0\vert_\Sol}{N}
   									\end{displaymath}
   							\end{itemize}   							 
   					\end{enumerate}
   				 
   				 \item Symplectic structure: endow the space $\Obs$ just defined with a bilinear form $\tau$.
   				   	\begin{enumerate}
   						\item Construct the Peierls Brackets between any pair of Lagrangian densities.\\
   							The construction is guaranteed by the requirement in step [\ref{Step:ClassicalDynamicsConditions}].
   						\item Restrict the brackets to the space $\Obs_0$.\\
   							These are very simple Lagrangian functionals:
   							\begin{displaymath}
   								Q_\chi \cdot = (\chi, \cdot) \qquad \forall \chi \in \Obs_0
   							\end{displaymath}
							such that:
							\begin{equation}\label{Def:SymplecticTau}
								\tau ( \phi, \psi) = ( \phi, E \psi)
							\end{equation}
							Conditions of Green-hyperbolicity and formally self-adjoint are sufficient guarantees the good definitions of $\tau$
							\footnote{Has to be noted that the Lagrangian condition is ancillary. This has the purpose to justify the shape of the symplectic form on the classical observables space as consequent from the Peierls bracket.
		\\
	It is frequent\cite{Dewitt1999}\cite{Benini} to overlook to the origin of this object and jump directly to the expression \ref{Def:SymplecticTau}  in term of the Green's operator that no longer present any direct link to the Lagrangian and therefore can be extended to any green-hyperbolic theory.}
						\item Finally the value of $\tau$ is transported to the equivalence classes of $\Obs$ evaluating on the representative:
							\begin{equation}
								\{ [\phi], [\psi]\} \coloneqq \tau(\phi, \psi)
							\end{equation}
							such that:
							\begin{itemize}
								\item $\{\cdot,\cdot\}$ is a simplectic form ( bilinear, antisymmetric, non-degenerate).
								\item Definition is well-posed: do not depend from the representative of the class.
								\item causality axiom
								\item time-slice axiom
							\end{itemize}
   					\end{enumerate}
   			\end{enumerate}
  
   		\item Quantization Step
   		   	\begin{enumerate}
   				\item Quantum Observables Algebra\\
   					A concrete realization is achieved in three step.
   					\begin{enumerate}
   						\item Construct the \emph{Universal Tensor Algebras} of the classical observables.
   						\item
   					\end{enumerate}
   					
   				\item Hadamard State
   				   	\begin{enumerate}
   						\item
   						\item
   					\end{enumerate}
   				 
   			\end{enumerate}
 	\end{enumerate}
 	
	\begin{observation}
		Conditions of Green-hyperbolicity and formally self-adjoint are sufficient guarantees the good definitions of $\tau$.
		Has to be noted that the Lagrangian condition is ancillary. This has the purpose to justify the shape of the symplectic form on the classical observables space as consequent from the Peierls bracket.
		\\
	It is frequent\cite{Dewitt1999}\cite{Benini} to overlook to the origin of this object and jump directly to the expression \ref{Def:SymplecticTau}  in term of the Green's operator that no longer present any direct link to the Lagrangian and therefore can be extended to any green-hyperbolic theory.
	\end{observation}
	
	\begin{Warning}
		Sull'inner product:\\
						Together with the Green-hyperbolicity this condition guarantees that $\exists 1! G^\pm$ and $(G^\pm)^\dagger) = G^\mp$.
				( $\exists 1! E$ causal propagator and $E^\dagger =  -E$.
	\end{Warning}
 	
 	\section{Quantizzazione dati iniziali}
 			\subsubsection{PreQuantum Step.}
	\begin{Warning}
		Si definisce la forma simplettica direttamente su  un opportuno sottoinsieme di data detto "spazio delle fasi classico.\\
		Gli osservabili classici (lineari) vengono definiti di conseguenza.\\
		Si prova che $\Obs$ così costruito è $\simeq$ $\Obs$ con le Peierls.\\
		Ma ciò che non è limpido è il rapporto tra le 2 parentesi costruite sui due spazi isomorfi ( quindi in sostanza su un sistema classico quantizzabile con entrambe le procedure differiscono solo per la diversa prescrizione sulla forma delle brackets)\\
		
		Va Illustrato il parallelismo (p.14 p.16 wald) con i sistemi a finiti gradi. questo esplica come la struttura simplettica definita su TT*Q X TT*Q si confonda con quella delle parentesi di Poisson def su $\Obs \times \Obs = \Sigma^\infty \times \Sigma^\infty$ nel caso di sistemi fisici lineari.
		
		Nell'applicazione di queste 2 procedure  per il campo di Jacobi sono da stressare i seguenti fatti:
		\begin{itemize}
			\item come interviene il fatto che la varietà base sia semplice $M= \Real$ .\\
				I dati iniziali sono numeri
			\item Come interviene l'imput che nello specifico l'eq del moto è data da Jacobi?\\
				(interviene in modo centrale  Riemman-Metrica-Pairing)
		\end{itemize}
		
		Si dice che le Peierls sono automaticamente covarianti (vedi ForgerRomero quando ne parla) mentre quelle sui dati iniziali rompono la covarianza:
		Di base c'è la scelta di una superficie di cauchy su cui dare i dati.
		
		Attenzione ad usare Wald!  è poco formalizzato: e.g.: non parla mai di  green hyperbolic ( anche perchè non serve!) conta solo che il problema di cauchy sia ben posto.
		
		CD parla dei Norm Hyperbolic che sono entrambe le cose!
		
		Quando costruisco C.F.S. scelgo i dati iniziali a supporto compatto.
			\begin{itemize}
				\item Motivazioni a posteriori è chara: garantisce la separabilità nel senso che una misurazione di tutte loro garantisce di esaustire la separabilità (cioè identificare in modo univoco una configurazione)
				\item c'è motivazione a priori? no, è pura praticità: abbastanza semplice da maneggiare + garantisce la separabilità. dunque è scelta minimale: situazione più semplice per fare il pairing. ( se avessi voluto complicarmi la vita avrei preso le distro a supporto compatto
				\item nella scelta non c'entra il fatto che le sup compatto sono funzioni di test, dunque sono il duale delle distribuzioni come dati iniziali.
			\end{itemize}
		\end{Warning}
				\paragraph{Symplectic Structure on the Phase Space}
				[Initial data symplectic form]			
			\begin{Warning}
				Proposta di definizione per dinamiche di ordine più alto..
				\begin{displaymath}
					\Omega \biggr\{ [f_0,\ldots, f_k] , [g_0,\ldots, g_k] \biggr\} =
					\int_\Sigma d\Sigma  \biggr(-\epsilon^{ab}(f_a,g_b) \biggr)
				\end{displaymath}
				gli indici corrono da (0, k-1) dove k è l'ordine... (anche se non ha senso \\
				Non va bene perchè non riesce a tenere conto del campo di Dirac!
			\end{Warning}
	\subsection{Quantum Step}
	   		\paragraph{Hadamard state} 
			Considering the scope of this thesis, we will focus primary on the first step. For a brief account on the construction of the \emph{quantum states} see Ref. \cite{Benini2013}.

			\begin{Warning}
			Non devi certo entrare nei dettagli, ma devi quantomeno accennare al fatto che siano la classe corretta di stati di usare in quanto godono di proprietà rilevanti quali in particolare la possibilità di costruire i polinomi di Wick in modo covariante.
				Fonti: 
				\begin{itemize}
					\item Advances:\\
						" one selects a state, that is a positive, normalized, linear functional on the algebra which allows us to recover the standard probabilistic interpretation of quantum theories via the GNS theorem."
					\item Primer : 
						\begin{itemize}
							\item The second step consists of selecting a so-called algebraic state $\omega$ that is a continuous linear and positive functional on A, which, via the GNS theorem,53 allows us to recover the interpretation of the elements of A as linear operators on a suitable Hilbert space.
							\item  In a free quantum field theory on Minkowski spacetime, under the assumption to work at vanishing temperature, there exists a unique ground state which can be singled out thanks to the Poincarè group.63
								The relevance of the so-called Poincar´ e vacuum is enormous, being at the heart of the perturbative
methods out of which interactions are treated. 
								On the contrary, whenever the underlying manifold is no longer trivial, the lack of a sufficiently big group of isometries of the metric forbids the existence of a natural vacuum state. We will show, moreover, that most of the algebraic states are not even physically acceptable since they entail that the basic objects of perturbation theory, theWick polynomials, cannot be well-defined. 
								We shall identify, therefore, a distinguished subclass of states, called Hadamard states, which avoid these pathologies and are unanimously recognized as being the only physically significant ones.
							\item we introduce in Section 4 the notion of an algebraic state on the resulting quantum field theory and we prove the GNS theorem which allows us to interpret the said algebra in terms of linear operators on a suitable Hilbert space. 
								Hence we recover the standard interpretation of a quantum theory. Eventually we introduce some basic tools proper of microlocal analysis in order to characterize physically sensible states by means of the so-called Hadamard condition.
						\end{itemize}
					\item QuasiFree:\\
				\end{itemize}
			\end{Warning}

					\begin{Warning}
				\begin{itemize}
					\item punto della situazione: ci troviamo un'algebra astratta (avremmo potuto impostare così anche la m.q.o) vogliamo capire come rappresentarla per mezzo di operatori su un opportuno spazio di hilbert . 
					dando interpretazione dell'azione dell'osservabile sugli stati.\\
					In the last part of this review we introduce the notion of algebraic state and the criteria which allow us to select those which are physically sensible.
					\item si definisce lo stato algebrico.\\
						l'idea che sta alla base della definizione di stato in questo modo è che 
						 - interpretando w(a) come il valore d'aspettazione dell'osservabile per un sistema nello stato omega-  
						per ogni osservabile a= a*  se conosco tutti i "momenti" e tutti i valori aspettazione sui polinimi costruiti con a è nota (ovvero posso ricostruire da questi) la distribuzione di probabilità relativa ai valori di outcome associati all'osservabile a. (per ora l'osservabile è astratto quindi gli outcome sono boh)
					\item per capire dove si vuole arrivare bisogna ricordare cos'è una rapresentazione di un unital * algebra
						
				\end{itemize}
			\end{Warning}

				\begin{definition}[Algebraic State]
					We call an \emph{(algebraic) state} over $\ObsAlg$ the $\Complex-$linear functional $\omega: \ObsAlg \rightarrow \Complex$ such that:
					\begin{itemize}
						\item it is positive:
							$$ \omega( a^* a ) \geq 0 \qquad \forall a \in \ObsAlg$$
						\item it is normalized:
							$$ \omega(\IdElem) = 1 $$	
					\end{itemize}									
				\end{definition}
			
				\begin{Warning}
					Aggiunge Moretti sotto la definizione\\
						
				 	The overall idea underlying this definition is that if, for a given observable $a = a^* \in \ObsAlg$ we know all moments $\omega( a^n )$, and thus all expectation values of polynomials $\omega\left(p(a)\right)$, we also know the probability distribution associated to every value of a when the state is $\omega$. 
				 	To give a precise meaning to this idea, we should represent observables a as self-adjoint operators $\hat{a}$ in some Hilbert space $H$, where the values of a correspond to the point of spectrum $\sigma(\hat{a})$and the mentioned probability distribution is that generated by a vector $\psi$  state representing $\omega$ in $H$, and the spectral measure of $\hat{a}$. 
				 	We therefore expect that, in this picture, $\omega(a) = \left\langle  \psi \vert \hat{a} \psi \right\rangle$ for some normalized vector $\psi \in H$. 
				 	This is, in fact, a consequence of the content of the celebrated GNS reconstruction procedure for unital C$\ast-$algebras [29, 60, 50].
				 	We will discuss shortly the unital  $\ast-$algebra version of that theorem. 
				 	Note that the general problem of reconstructing even a unique classical state (a probability distribution on phase space) from the knowledge of all of its polynomial moments is much more difficult and is sometimes impossible (due to non-uniqueness). 
				 	This kind of reconstruction goes under the name of the Hamburger moment problem [55, X.6 Ex.4].
				\end{Warning}					
			
\section{Raccordo tra le due procedure}

	%\subsection{Equivalence of the Brackets}	
	\begin{proposition}[The mapping $\Xi$ is a simplettomorphism.]
		Let be $(\Obs,\tau)$ and $(\Obs_{Lin},\Omega)$ the two classical symplectic spaces according to initial data quantization and Peierls quantization, where
		\begin{displaymath}
			\sigma: \Sol_{sc}\times \Sol_{sc} \rightarrow \Real \qquad 
			\sigma\big( \psi, \phi \big) \int_\Sigma \big( <\nabla_n \psi ,\phi>  - <\psi, \nabla_n \phi> \big) d\Sigma
		\end{displaymath}
		\begin{displaymath}
			\tau: \Obs \times \Obs \rightarrow \Real \qquad
			\tau \big( [f] ,[g] \big) = \int_M < f, Eg> d\mu
		\end{displaymath}
		are the corresponding symplectic forms.\\
		The isomorphism $\Xi: [f] \mapsto E f$ between the two underlying vector spaces preserves the symplectic forms:
		\begin{displaymath}
			\sigma \big( Ef, Eg \big) =  \tau\big( [f], [g] \big)
		\end{displaymath}
		
	
	\end{proposition}
	\begin{proof}
		\danger non vale in generale ma solo per alcuni casi!
	\begin{Warning}
		La formula discende seguendo un ragionamento simile a quello precedente. Nota che vale per P operatore d'onda (o di KG) e non in generale per ogni operatore Green-iperbolico e formalmente autoaggiunto (ad esempio per Dirac non vale, seppur sia un operatore Green iperbolico).
	\end{Warning}
		\begin{align}
		\tau\big( [f], [g] \big) \coloneqq  & \int_M f E h d\textrm{Vol}_M = 
		\int_{\CausalFut(\Sigma)} f \psi d\textrm{Vol}_M	 + \int_{\CausalPast(\Sigma)} f \psi d\textrm{Vol}_M =	\nonumber \\
		=& \int_{\CausalFut(\Sigma)} (P \GreenAdv f) \psi d\textrm{Vol}_M	 + \int_{\CausalPast(\Sigma)} ( P \GreenRet f ) \psi d\textrm{Vol}_M =	 \\
		=&  -\int_\Sigma \big( \nabla_n ( \GreenAdv f) \big) \psi d\Sigma
		+\int_\Sigma \big( ( \GreenAdv f) \big)\nabla_n  \psi d\Sigma +\\
		&+\int_\Sigma \big( \nabla_n ( \GreenRet f) \big) \psi d\Sigma  
		-\int_\Sigma \big( ( \GreenRet f) \big)\nabla_n  \psi d\Sigma =  \\
		=& \int_\Sigma \big( \phi \nabla_n \psi - \psi \nabla_n \phi \big) d\Sigma \coloneqq\sigma (\phi, \psi)
		\end{align}

	\end{proof}

%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
\chapter{Jacobi Fields}
%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
\section{intro}
	ho definito la geodesica come curva smooth.. in realtà basta essere piecewise $C^2$!
	
\section{Geodesic Problem as a Mechanical Systems}
	\begin{observation}
		The geodesic system is not simply Lagrangian but also Hamiltonian.
		This property follows from the hyperregularity\cite{Abraham1978} of $L$.
		
		\begin{Warning}
		Anyway we will neglect this fact inasmuch in what follows only the Lagrangian character assumes a role.
		\end{Warning}
	\end{observation}
\section{Geodesic Peierls}
	
	\begin{Warning}
	Introduzione da rividere, dimostro che l'operatore linearizzato senza termine inomogeneo corrisponde all'equazione di Jacobi vera e propria mentre con termine inomogeneo dato dalle E-P del disturbo da l'equazione che definisce la perturbazione ritardata e anticipata.
	\end{Warning}

	\begin{Warning}
		Da dire: espressione in coordinate della lagrangiana, è altmente non lineare perchè implicitamente è $g_{\mu\nu}(\gamma^i(t))$ non polinomiale in $\gamma^i$ ed esplicitamente è quadratica, Mostrare esplicitamente che l'equazione di jacobi per il sistema è effittivamente l'equjazione di jacobi ( questo è triviale se vedi come definisce il campo di jacobi jurgen 
	\end{Warning}	
	
	\begin{Warning}
		Sul quaderno ho scritto un po' di più ma in un modo non adatto alla tesi.! peccato
	\end{Warning}	
		
\section{Jacobi Quantization}
			Operator $P$ ruling the dynamics is formally self-adjoint:
				\begin{displaymath}
				 ( Y, PX) = \int Y_\mu PX^\mu dt= 
				 \int\left( Y_\mu \ddot{X}^\mu + Y_\mu R^\mu_{\, i \alpha j}T^i T^j X^\alpha \right)dt =
 				 \int\left( \ddot{Y}_\mu X^\mu + X_\mu R^\mu_{\, i \alpha j}T^i T^j Y^\alpha \right)dt =
				 \int P Y_\mu X^\mu dt=( PY, X) 				 				 
				\end{displaymath}
			where is been integrated by parts twice (border value are null since the integrand is compactly supported) and has been exploited a curvature tensor identity:
				\begin{displaymath}
					\langle R(X,T)T,Y \rangle = \langle R(Y,T)T,X \rangle
				\end{displaymath}
				Uso nell'ordine:
				\begin{eqnarray}
					& 	\langle R(u,v)w,z \rangle=\langle R(w,z)u,v \rangle		\\
					&	R(u,v)=-R(v,u) \\
					& \langle R(u,v)w,z \rangle=-\langle R(u,v)z,w \rangle
				\end{eqnarray}

\chapter{Interpretations}
	\section{Spunti degli Esperti}
		\subsection{Forger Romero}
			\paragraph{Intro}
			One of the most annoying flaws of the usual canonical formalism in field theory is its lack of manifest covariance, that is, its lack of explicit Lorentz invariance (in the context of special relativity) and more generally its lack of explicit invariance under space-time coordinate transformations (in the context of general relativity). 
			
			This defect is built into the theory from the very beginning, since the usual canonical formalism represents the dynamical variables of classical field theory by functions on some spacelike hypersurface (Cauchy data) and provides differential equations for their time evolution off this hypersurface: thus it presupposes a splitting of space-time into space and time, in the form of a foliation of space-time into Cauchy surfaces.
			
			As a result, canonical quantization leads to models of quantum field theory whose covariance is far from obvious and in fact constitutes a formidable problem: as a well known example, we may quote the efforts necessary to check Lorentz invariance in (perturbative) quantum electrodynamics in the Coulomb gauge. \\
			These and similar observations have over many decades nourished attempts to develop a fully covariant formulation of the canonical formalism in classical field theory, which would hopefully serve as a starting point for alternative methods of quantization.
			
			Among the many ideas that have been proposed in this direction, two have come to occupy a special role. 
			\begin{itemize}
				\item  One of these is the “covariant functional formalism”, based on the concept
				of “covariant phase space” which is defined as the (infinite-dimensional) space of solutions of the equations of motion. 
				This approach was strongly advocated in the 1980’s by Crnkovi´c,Witten and Zuckerman [1–3] (see also [4]) who showed how to constructa symplectic structure on the covariant phase space of many important models of field theory (including gauge theories and general relativity).
				
				The covariant functional formalism fits neatly into the philosophy underlying the symplectic formalism in general; in particular, it admits a natural definition of the Poisson bracket (due to Peierls [16] and further elaborated by DeWitt [17–19]) that preserves the duality between canonically conjugate variables. 
				Its main drawback is the lack of mathematical rigor, since it is often restricted to the formal extrapolation of techniques from ordinary calculus on manifolds to the infinite-dimensional setting: transforming such formal results into mathematical theorems is a separate problem, often highly complex and difficult.
				\item The other has become known as the “multisymplectic formalism”, based on the concept of “multiphase space”... (non ci interessa per questa tesi)
\end{itemize}			

		\subsection{Marolf}
			In 1952, R.E. Peierls noticed that an algebraic structure equivalent to the Poisson bracket could be defined directly from any action principle without first performing a canonical decomposition into coordinates and momenta. 
			His essential insight was to consider the advanced and retarded “effect of one quantity (A) on another (B).” Here, A and B are to
be functions on H. 

			L'effetto in poche parole:\\
			The advanced  and retarded  effects of A on B are then defined by comparing the original system with a new system defined by the action $S_\epsilon = S + \epsilon A$ and the same space H of histories. 
			Under retarded (advanced) boundary conditions for which the solutions $\phi \in S$ and $\phi_\epsilon	\in S_\epsilon$ coincide to the past (future) of the support of A, the quantity $B_0 = B(\phi)$ computed using $\phi$ will in general differ from $B_\epsilon = B(\phi_\epsilon)$ computed using $\phi_\epsilon$
For small epsilon, the difference between these quantities defines the retarded (advanced) effect of A on B through:
which depends on the unperturbed solution $\phi$.
	\section{Il discorso dell'interpretazione geometrica visto come la \emph{MECCANICA GEOMETRICA} dei sistemi campo}
		La parola chiave è \emph{Covariant Phase Space}, Forger-ROmero danno spunti su questa idea ma io sono ancora troppo impreparato per coglierli a pieno.\\
		Spunti interessanti sono qua \url{http://ncatlab.org/nlab/show/phase+space}
		\\
		Questo discorso è fortemente legato alle parentesi di Peierls. di base c'è un po' l'obbiettivo di identificare le varietà simplettiche come il fondamento un po' di tutto.. quindi anche per i sistemi tipo campo!
		Se si decide che lo spazio simplettico è Sol allora la forma simplettica la si costruisce con  Peierls!
		
		
%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
\chapter{Test}
%\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/
	$$L - \mathrm{L} - \mathit{L}  - \mathbf{L} - \mathsf{L} - \mathtt{L}- \mathcal{L}- \mathbb{L}- \mathfrak{L}$$



\end{document}