\documentclass[Cascione]{subfiles}
\begin{document}
\chapter{Cascione Interpretazione Geometrica}

%\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/
%						INTRODUZIONE
%\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/
	\begin{Warning}
		Riguardo il problema dell'interpretazione geometrica ho raccolto una cartelletta nel quaderno in cui commento anche quanto scritto qui. Non c'è tempo per mettere quei pensieri in digitale!
	\end{Warning}


	\paragraph{Visione Globale preliminare}
		\begin{itemize}
			\item 		è evidente che una costruzione così articolata non si presta ad un'interpretazione geometrica immediata.
			\item 		Ciò che mi sfugge un po' è in che modo jacobi ci aiuta a dare  un'interpretazione geometrica.
			\item		Keyword: covariant phase space...  Forger ROmero è pieno di spunti interessanti anche Khavkine... ma mi sembra chiaro che qualsiasi interpretazione geometrica non scampi da un pesante inserto di teoria dei campi classici (variational bicomplex and so on)
			\item		Il grande open problem di questo formalismo geometrico è che molti punti sono calcolo formale tirato di peso dalla teoria a gradi finiti la cui corretta definizione matematica latita.. Analisi globali e teoria delle variazioni vera.
		\end{itemize}

	\paragraph{Organizzazione del Capitolo}
		\begin{itemize}
			\item Geometric Visualization\\
				Serie di immagini per spiegare in cosa consiste l'algoritmo di Peierls
			\item Geometric interpretation of Geodesic Bracket \\
				Spiegare il discorso di Cd sulle motivazioni che spingono a cercare un'interpretazione geometrica al tutto. (vedi sotto)
			\item Geometric mechanics of prequantum field theory.
				\begin{itemize}
					\item cos'è la meccanica geometrica in generale
					\item si può fare per i campi?
				\end{itemize}
		\end{itemize}



%\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/
	\newpage
	\section{Pitturizzazione Geometrica}
%\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/
		ok, manca un po' di conclusione riguardo l'ultimo punto....



%\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/
	\newpage
	\section{Constestualizzazione Geometrica}
%\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/
	\begin{itemize}
		\item 	Essenzialmene c'è da parlare del Covariant Phase space. Prima di tentare un'interpretazione geometrica penso sia utile fornire una carrellata sulla meccanica geometrica dei sistemi campo.
		\item 	Il tentativo che vogliamo fare è quello di identificare in modo preciso la struttura geometrica delle parti coinvolte.
		\item Questo tentativo è ancora in atto ed è stato "This approach was strongly advocated in the 1980’s by Crnkovic, Witten and Zuckerman who showed how to construct a symplectic structure on the covariant phase space of many important models of field theory" (Forger Romero)
		\item Il tema presenta ancora notevoli aspetti controversi dal punto di vista dell'analisi globale.
	\end{itemize}
	
	\begin{Warning}
		La parola chiave è \emph{Covariant Phase Space}, Forger-ROmero danno spunti su questa idea ma io sono ancora troppo impreparato per coglierli a pieno.\\
		Spunti interessanti sono qua \url{http://ncatlab.org/nlab/show/phase+space}
		\\
		Questo discorso è fortemente legato alle parentesi di Peierls. di base c'è un po' l'obbiettivo di identificare le varietà simplettiche come il fondamento un po' di tutto.. quindi anche per i sistemi tipo campo!
		Se si decide che lo spazio simplettico è Sol allora la forma simplettica la si costruisce con  Peierls!
	\end{Warning}	
	
	\begin{Warning}
		Ricordare: in questa Tesi non sono in grado di dare lo "stato dell'arte"  sulla meccanica geometrica dei campi quindi neanche sulle Parentesi di Peierls\\
		Il sistema campo pre quantistico più generico che si può costruire richiede due ingredienti ulteriori:
			\begin{itemize}
				\item Libertà di Gauge
				\item Spin structure
			\end{itemize}		
			L'idea è che tutta l'immagine precedente richiederebbe una further investigation from a mathematical point of view per essere ammessa come rigorosa.
	\end{Warning}
		
		
	\subsection{Spunti degli Esperti}
	
		\subsubsection{Spunti Sparsi}
	
			\begin{Warning}
			\underline{Crincovic}\cite{Crnkovic1999}\\
			So far, we have been talking about the \emph{Hamiltonian} description of the canonical formalism.
			Such a description demands, for the definition of the canonically conjugate momenta and the Hamiltonian, singling out a 'time' coordinate. 
			For Lorentz-invariant theories, and in particular field theories, that amounts to not keeping all of the symmetry manifest. 
		\end{Warning}
		
		\begin{Warning}
			\underline{Witten e crinkovic}\\
			The canonical approach is usually interpreted as an approach that ruins Poincarè invariance from the beginning through an explicit choice of "time" coordinate.
			This is not necessarily so, however. The essence of the canonical formalism can be developed in a way that manifestly preserves all the relevant symmetries.		
		\end{Warning}
		
		\begin{Warning}
			\underline{Witten e crinkovic}\\
			Osservazione chiave:
			classical solutions of any given physical theory, in any given coordinate system, are in one-to-one correspondence with the value of $P_s$ and $q_s$ at time zero.
			
			This lead us to a manifestly covariant phase space as the spade of solutions of the classical equations.
		\end{Warning}
		
		\begin{Warning}
			\underline{Crincovic}\cite{Crnkovic1999}\\
			L'idea chiave è il legame tra phase space e data
			
			Remember that the solutions of the equations of motion are labelled by the chosen initial values. 
			That is, in a sufficiently well behaved system, there is a one-to-one correspondence between the solutions of the equations of motion and the values of p and q at time zero. 
			This leads us to the central idea of our approach [Witt crink 300 years] for any well behaved system, points in the phase space are the solutions of the classical equations of motion, i.e. classical phase space is the space of the solutions of the classical equations. For a Lorentz-invariant theory, this definition of the classical phase space is manifestly covariant.		
			
			It remains to investigate precisely what 'well behaved' means in this context.
			Obviously, we need systems that, for each point in the phase space, have one and only one direction of the Hamiltonian flow.
		\end{Warning}	
		
		\begin{Warning}
		\underline{Crincovic}\cite{Crnkovic1999}\\
		Assuming that all is well, and we are able to set up the covariant phase space, we should note that identifying points of the phase space with whole solutions of the equations of motion requires a conceptual shift in thinking about the time development of the system.
		In the standard Hamiltonian framework one identifies solutions of the equations of motion with integral curves of the Hamiltonian vector fields. 
		In the covariant phase space that identification, obviously, becomes untenable. But that does not prevent us from explicitly studying the time development of a system by studying its Hamiltonian vector fields. 
		The difference is that now we interpret the Hamiltonian flow as taking us from one solution to a diferent solution infinitesimally removed from it	
		\end{Warning}

		\begin{Warning}
			\underline{Khavkine}\cite{Khavkine2014}\\
			While symplectic and Poisson structures are obviously related, as can be seen from the above references, the two covariant formalisms that we have described naturally appear in somewhat different problems. 
			Thus, it is not surprising that most researchers would prefer to use just one or the other, without attempting to relate the two.
			 Some have actually done so, though, until recently only using the fact that they are both equivalent (under appropriate assumptions of course) to the corresponding canonical constructions.
			 
			 rather recently, a breakthrough appeared in a paper of Forger andRomero. They managed to prove the equivalence of the covariant constructions of the symplectic and Poisson structures in an elegant and fully covariant way, thus without using the canonical formalism as an intermediary.

		\end{Warning}		
		
		\begin{Warning}
			\underline{Parte Scopiazzata dalle fonti che va parafrasata}:\\

			The covariant phase space of a system in physics is the space of all of its solutions to its classical equations of motion, the space of classical trajectories of the system. 
			Typically these phase spaces are (locally) naturally parameterized by the suitable boundary conditions or choice of a Cauchy surface which uniquely determine the corresponding history of the physical system. This parameterization is what traditionally is just called a “phase space”. 
			The “covariant” in “covariant phase space” is to indicated that it comes without any unnatural choices.
	
			For instance for a non-relativistic particle propagating on a Riemannian manifold $X$ with the usual action functional, a trajectory is uniquely fixed by the position $x_i \in X$ and the momentum $p\in T^*_x X$ of the particle at a given time. 
			Correspondingly the space of all solutions and hence the (covariant) phase space of the system may be identified with the cotangent bundle $T^*X$ of $X$.

 			The covariant phase space can be embedded into the space of field configurations as a subspace of the set of solutions that intersects transversely gauge orbits.  
			This embedding is characterized as the zero locus of the equations of motion and some gauge fixing conditions. The non-degenerate Poisson structure on the algebra of functions on the covariant phase space is given by the Peierls bracket.
		\end{Warning}

		\begin{Warning}
			\underline{Parte Scopiazzata dalle fonti che va parafrasata}:\\
			The Peierls bracket between two functions $A$ and $B$ is the antisymmetrized influence on $B$ of an infinitesimal perturbation of a gauge-fixed action by a function that restricts to A on the embedding. 
			The algebra of functions on the space of field configurations becomes a Poisson algebra in the following way. Pick a set of functions on the space of field configurations that restrict to a non-degenerate coordinate system on the embedded covariant phase space.
			These functions, together with the equations of motion and gauge fixing conditions define a Poisson bivector by being declared canonical, so that the kernel of the bivector coincides with the ideal generated by the equations of motion and the gauge fixing conditions.
			The Poisson structure thus constructed on the algebra of functions on field configurations is not unique and depends on the above choice of coordinates; the same non-uniqueness may be parametrized instead by a choice of a connection on the space of field configurations.
			The embedded covariant phase space becomes a leaf of the symplectic foliation of the space of field configurations.

			However, even reduced phase spaces are not all cotangent bundles, for instance, if they are obtained by symplectic reduction.
			In this way a finite-dimensional phase space can sometimes describe continuous systems (e.g. in hydrodynamics) which have infinitely many degrees of freedom; that phase space is however not a cotangent bundle in general.
		\end{Warning}

		\begin{example}
			The covariant phase space of the relativistic particle on a pseudo-Riemannian manifold X is the space of geodesics of X (in the absence of a background gauge field).
		\end{example}

		\begin{Warning}
			\underline{Khavkine}\cite{Khavkine2014}\\
			(It is needed) a serious functional analytical effort to describe the infinite dimensional spaces of field configurations and algebras of observables using infinite dimensional differential geometry.
		\end{Warning}				

		\begin{Warning}
			\underline{Khavkine}\cite{Khavkine2014}\\
			It is likely that Peierls was guided by experience. Having seen the unequal time Poisson bracket (or rather the quantum commutator) of point fields in many examples, computed using the canonical method, but expressed in relativistically invariant form, he was probably lead to a guess for its general formula. 
			He showed that this formula is in fact antisymmetric and is equivalent to the canonical bracket for equal time fields, in the non-singular case (without gauge invariance). 
		\end{Warning}		
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
			\subsubsection{Crnkovic Witten}
			The essence of the canonical formalism can be developed in a way that naturally preserves all natural symmetries, including Poincarè invariance.
			
			Let us recall the main steps in the canonical formalism of a theory with $N$ degrees of freedom.
			\begin{itemize}
				\item  One usually introduces coordinates $q^j$and conjugate momenta $p^i$
				\item One defines the two-form $\omega = dp^i \wedge dq^i$
				\item For the sake of commodity it is convenient to combine $p^i, q^j$ in a variable $Q^I , I = 1,\ldots,2N$, with $Q^i=p^i$ for $i\leq\leq N$ and $Q^i= q^{i-N}$ for $i>N$.\\
					one can think of $\omega$ as an antisymmetric $2N \times 2N$ matrix $\omega_{I J}$ whose non-zero matrix elements are $\omega_{i, i+N} = - \omega_{i+N,i}= 1$.
				\item One defines the Poisson bracket of any two functions $A(Q^I) , B(Q^J)$ by:
					\begin{displaymath}
						\left[ A , B \right] = \omega^{I J} \frac{partial A}{\partial Q^I} \frac{\partial B}{\partial Q^J}
					\end{displaymath}
			\end{itemize}
	
		\subsubsection{Forger Romero}
			One of the most annoying flaws of the usual canonical formalism in field theory is its lack of manifest covariance, that is, its lack of explicit Lorentz invariance (in the context of special relativity) and more generally its lack of explicit invariance under space-time coordinate transformations (in the context of general relativity). 
			
			This defect is built into the theory from the very beginning, since the usual canonical formalism represents the dynamical variables of classical field theory by functions on some spacelike hypersurface (Cauchy data) and provides differential equations for their time evolution off this hypersurface: thus it presupposes a splitting of space-time into space and time, in the form of a foliation of space-time into Cauchy surfaces.
			
			As a result, canonical quantization leads to models of quantum field theory whose covariance is far from obvious and in fact constitutes a formidable problem: as a well known example, we may quote the efforts necessary to check Lorentz invariance in (perturbative) quantum electrodynamics in the Coulomb gauge. \\
			These and similar observations have over many decades nourished attempts to develop a fully covariant formulation of the canonical formalism in classical field theory, which would hopefully serve as a starting point for alternative methods of quantization.
			
			Among the many ideas that have been proposed in this direction, two have come to occupy a special role. 
			\begin{itemize}
				\item  One of these is the “covariant functional formalism”, based on the concept 	of “covariant phase space” which is defined as the (infinite-dimensional) space of solutions of the equations of motion.
					This approach was strongly advocated in the 1980’s by Crnkovi´c,Witten and Zuckerman [1–3] (see also [4]) who showed how to constructa symplectic structure on the covariant phase space of many important models of field theory (including gauge theories and general relativity).
				
					The covariant functional formalism fits neatly into the philosophy underlying the symplectic formalism in general; in particular, it admits a natural definition of the Poisson bracket (due to Peierls [16] and further elaborated by DeWitt [17–19]) that preserves the duality between canonically conjugate variables. 
					Its main drawback is the lack of mathematical rigor, since it is often restricted to the formal extrapolation of techniques from ordinary calculus on manifolds to the infinite-dimensional setting: transforming such formal results into mathematical theorems is a separate problem, often highly complex and difficult.
					
				\item The other has become known as the “multisymplectic formalism”, based on the concept of “multiphase space”... (non ci interessa per questa tesi)
			\end{itemize}			

		\subsubsection{Marolf}
			In 1952, R.E. Peierls noticed that an algebraic structure equivalent to the Poisson bracket could be defined directly from any action principle without first performing a canonical decomposition into coordinates and momenta. 
			His essential insight was to consider the advanced and retarded “effect of one quantity (A) on another (B).” Here, A and B are to
be functions on H. 

			The advanced  and retarded  effects of A on B are then defined by comparing the original system with a new system defined by the action $S_\epsilon = S + \epsilon A$ and the same space H of histories. 
			Under retarded (advanced) boundary conditions for which the solutions $\phi \in S$ and $\phi_\epsilon	\in S_\epsilon$ coincide to the past (future) of the support of A, the quantity $B_0 = B(\phi)$ computed using $\phi$ will in general differ from $B_\epsilon = B(\phi_\epsilon)$ computed using $\phi_\epsilon$.
			For small epsilon, the difference between these quantities defines the retarded (advanced) effect of A on B through:
which depends on the unperturbed solution $\phi$.

	\subsection{Meccanica Geometrica per i campi}
		Bisogna ricordare cosa si intende per meccanica geometrica per spiegare cosa si intende per meccanica geometrica per i sistemi prequantum.
	
	 	\subsubsection{Lessing}
			\begin{itemize}
				\item Geometric mechanics employs modern geometry to describe mechanical systems.\\
					But how does geometry arise in mechanics?  (lessig)
				\item We begin to see how geometry is an intrinsic part of mechanics and why the geometry should be respected: the space of all admissible configurations of a mechanical system has a natural geometric structure and constraints are intrinsically satisfied by the choice of the geometry. 
				In more formal parlance, the configuration space Q of a mechanical system is a manifold, the generalization of a 2-dimensional surface in space, and its topological and geometrical structure represent all physical states.
				The description of the configurations of a system as points on a manifold is the principal premise of geometric mechanics and it enables to illustrate the system’s structure even when the configuration space is complicated and abstract, cf. again Table 1, providing the inherent intuition of geometric mechanics.
			\end{itemize}
			
		\subsubsection{Idea Mia}
			\begin{itemize}
				\item la scommessa della meccanica geometrica è quella di poter attribuire ad ogni sistema meccanico una varietà simplettica anche nota come spazio della fasi.
				\item la pretesa implicita è che da tale spazio delle fasi si possa ricavare tutto, e in meccanica classica lo si fa una volta fissata la scelta di una hamiltoniana.
				\item Vogliamo estendere questo ragionamento ai campi.. qual'è lo spazio delle fasi per un sistema campo?
				\item Ci sono due grandi scogli
					\begin{itemize}
						\item mentre per il sistema classico a gradi finiti la scelta della varietà è limpida ( i vincoli determinano lo spazio delle configurazioni e da quello si costuisce lo spazio delle fasi come fibrato cotangente) per i campi non è così: Wald e peirels danno delle descrizioni diverse (che risultano equivalenti) la prima viene costruita esplicitamente come un ponte  con la meccanica geom a gradi finiti (vedere i punti dello spazio delle fasi come dati)
						\item in mec. punti la forma simplettica è una proprietà intrinseca della costruzione dello spazio delle fasi (ogni fibrato cotangente è simplettico) e il teorema di darboux fornisce un'espressione univoca.
							Inoltre, fissato un dato, l'hamiltoniana fissata determina una traiettoria come flusso del campo hamiltoniano.\\
							Per i campi non ho tutti questi lussi				
					\end{itemize}
				\item bisogna far notare una cosa importante: in tutto questo c'è il tema di passare dallo spazio della fasi (inteso come spazio dei dati iniziali) al cosidetto spazio delle fasi covariante.\\
					Questo dovrebbe essere SOL, ed ho mostrato come Sol esista per ogni sistema meccanico indipendentemente dalla cardinalità delle coordinate di configurazione.
			\end{itemize}		


%\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/
	\newpage
	\section{Il Problema dell'interpretazione Geometrica Vero e proprio}
%\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/\_/
		At this point should be clear to the reader how the Peierls constructions is tutt'altro che limpida.
		


		\subsection{Interpretazione Geometrica nell'accezione di CD}
			\begin{itemize}
				\item Abbiamo raccontato come si costruisce lo spazio simplettico per le teorie di campo secondi i due approcci alla Peierls e alla Wald.
				\item  Abbiamo provato che i due spazi simplettici sono isomorfi ma sono simplettomorfi solo in alcuni casi particolari.
				\item entrambe le due costruzioni sono esoteriche e calate dall'alto. 
					Mediamente vengono utilizzate come "black box" come ricette per dare una forma simplettica utile ma:
				\begin{itemize}
					\item a priori non c'è nessun motivo per cui le forme simplettiche che forniscono siano quelle "giuste".
					\item I singoli passaggi della costruzione non hanno giustificazione fisica.
					\item 	In breve: sappiamo il come, sappiamo che funziona ma non sappiamo "perchè".
				\end{itemize}
				\item Perchè Jacobi è un esempio pregnante?\\
					In questo caso la costruzione di Wald non è ambigua. Data è isomorfo a $\Real^(2n)$ e la forma $\Sigma$ che viene imposta dalla procedura di wald corrisponde all'unica scelta possibile prevista dal teorema di Darboux (notare che anche per il semplice campo scalare lo spazio data è costituto da coppie di funzioni $C_0$ tutt'altro che finito dimensionale.
				\item l'interpretazione che cerchiamo è quasi di stampo "filosofico". Perchè la costruzione convoluta di peierls che parte dal considerare i disturbi lagrangiani è equivalente proprio all'unica forma simplettica su $Data=\Real^{2n}$ che praticamente coincide con lo spazio delle fasi classico?
				\item il problema sfuggente è "discutere sul perchè la costruzione di Peierls fornisce proprio la giusta usuale forma simplettica (parentesi $\Omega$) sullo spazio delle fasi classico?"\\
					( che su $\real^{2n} $ sono univocamente fornite dal teorema di Darboux)			
		\end{itemize}

		\subsection{Cosa abbiamo imparato dal caso evidenziato}
		Per quanto concerne "cosa abbiamo imparato" dal metodo di Peierls applicato ad i campi di Jacobi, l'idea di base era quella di confrontare questo metodo (Peierls) con quello dei dati iniziali in un caso particolare in cui lo spazio vettoriale dei dati iniziali sia finito dimensionale e quindi la struttura simplettica soggiacente sia unica, a fronte del teorema di Darboux. 
		Purtroppo si è evidenziato che il confronto dei due metodi non è così immediato come uno potesse sperare in quanto entra in gioco anche la perturbazione nello "spazio delle lagrangiane" la cui interpretazione geometrica non è così diretta. 

\end{document}